Formalizing Stack Safety as a Security Property\ifcameraready\else\vspace{-0.75cm}\fi

### 2023-05-12 submission5/core.tex
Writeup about Nick and Andre.

We implement and test two micro-policies from Roessler and DeHon~\cite{DBLP:conf/sp/RoesslerD18}:
{\em Depth Isolation} (\(DI\)) and {\em Lazy Tagging and Clearing} (\(LTC\)).
They share a common structure: each function activation is assigned a ``color'' \(n\)
representing its identity. Stack locations belonging to that activation are
tagged \(\tagStackDepth{n}\), and while the activation is running, the tag on the
program counter (PC tag) is \(\tagPCDepth{n}\). Stack locations not part of
any activation are tagged \(\tagNoDepth\).

@@

\paragraph*{Blessed Sequences}

@@

@@

Roessler and DeHon do not protect registers, since the compiler is in the
trusted computing base, but we support threat models that do not.
In particular, \(\clri\) requires callee-saved
registers to be saved and restored properly. We extend \(DI\) and \(LTC\)
so that callee-saved registers, too, are tagged with the color of the
function that is using them. In \(DI\) they are tagged as part of the entry
sequence, while in \(LTC\) they are tagged when a value is placed in them.

@@

\sna{Discuss the distinction that they make between memory safety and
  dataflow integrity; we have framed stack safety as a dataflow integrity
  problem. They did not give a formal specification, and their implementation
  does not enforce ours. Spell out the violation. Priority 1.}

>>>>

We implement and test two micro-policies inspired by
Roessler and DeHon~\cite{DBLP:conf/sp/RoesslerD18}:
{\em Depth Isolation} (\(DI\)) and {\em Lazy Tagging and Clearing} (\(LTC\)).
Their connections to Roessler and DeHon's work is discussed below.
They share a common structure: each function activation is assigned a ``color'' \(n\)
representing its identity. Stack locations belonging to that activation are
tagged \(\tagStackDepth{n}\), and while the activation is running, the tag on the
program counter (PC tag) is \(\tagPCDepth{n}\). Stack locations not part of
any activation are tagged \(\tagNoDepth\).

@@

@@

\paragraph*{Applicability to R\&D}

In Roessler and DeHon, Lazy Tagging and Lazy Clearing are both optimizations that
can be applied to their Depth Isolation policy. Our version of \(LTC\)
corresponds to Depth Isolation with both optimizations applied. How closely
do our properties correspond to the specifications of their policies?

Roessler and DeHon differentiate between memory safety policies (without lazy optimization)
and {\em data-flow integrity} policies (with lazy opimization.) Our properties
are phrased in terms of data flow, which corresponds to the optimized policies,
and which we argue is also sufficient to test non-optimized Depth Isolation.
Explicit formal properties are out of their scope, but they do list the
behaviors that they expect their data-flow integrity policies to prevent.
Data-flow integrity policies should prevent reads from sealed objects
(our caller confidentiality), should catch writes to sealed objects
if they are later read (our caller integrity), and should prevent reads
from deallocated objects (our callee confidentiality.)
They also note that Lazy Clearing prevents uninitialized reads,
which corresponds to our callee integrity.

They note a flaw in Data-flow Integrity: because function activations
are identified by depth, a dangling pointer into a stack frame might be usable
when a new frame is allocated at the same depth. Our testing does not discover
this flaw, because we do not test address-taken objects, but it discovers a
related flaw under Lazy Tagging and Clearing that does not require
an object's address to be taken. If an activation reads a location
that was previously written by an activation at the same depth, it will
violate callee confidentiality. If that location was in a caller's frame,
it also violates caller integrity and confidentiality.

Roessler and DeHon propose addressing the dangling-pointer issue by
tracking both the depth of the current activation and the identity
of the active function. This would not eliminate all instances, but it
would require the confidentiality-violating activation to be of the same
function that wrote the data in the first place, which is a significantly higher bar.
We propose instead tracking every activation uniquely, which in our tests eliminates
the issue entirely.

@@

Roessler and DeHon do not need to protect registers, since the compiler is in their
trusted computing base, but we target threat models that do not.
In particular, \(\clri\) requires callee-saved
registers to be saved and restored properly. We extend \(DI\) and \(LTC\)
so that callee-saved registers, too, are tagged with the color of the
function that is using them. In \(DI\) they are tagged as part of the entry
sequence, while in \(LTC\) they are tagged when a value is placed in them.

@@
